---
title: "Marathon Performance Analysis: Impact of Different Weather Conditions on Runners"
author: "William Qian"
date: "October 2024"
output: pdf_document
---

```{r setup, include=FALSE, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
library(mice, warn.conflicts = FALSE)
library(naniar)
library(ggplot2)
library(dplyr)
library(readr)
library(tidyr)
library(readxl)
library(ggpubr)
library(gtsummary)
library(GGally)
library(ggcorrplot)
library(knitr)
library(kableExtra)
library(lubridate)
library(patchwork)
library(introdataviz)

```

```{r load_data}
# Load data
marathon_data <- read.csv("../Data/project1.csv")
course_record <- read.csv("../Data/course_record.csv")

```

# Abstract

# Introduction

Marathon running is a popular sport that attracts millions of participants worldwide. The completion time of a marathon is influenced by various factors, including weather conditions. In this report, we analyze the impact of different weather conditions on marathon performance across the lifespan in both men and women using data from five major marathons: Boston, NYC, Chicago, Twin Cities, and Grandmas. 

# Data Description

Two datasets are used in this analysis: Marathon Data and Course Record Data. Those two datasets were combined to form a comprehensive dataset for analysis. 

### Marathon Data

The Marathon Data contains information about the average completion record percentage grouped by age and sex of runners in five major marathons: Boston, NYC, Chicago, Twin Cities, and Grandmas. The dataset includes the following columns:

| Parameter       | Coding details                                                                            |
|-----------------|-------------------------------------------------------------------------------------------|
| **Race**        | 0 = Boston Marathon , 1 = Chicago Marathon , 2 = New York City Marathon , 3 = Twin Cities Marathon (Minneapolis, MN) , 4 = Grandma’s Marathon (Duluth, MN) |
| **Year**        | Year of the marathon                                                                      |
| **Sex/Gender**  | 0 = Identified as Female , 1 = Identified as Male                                       |
| **Flag**        | White = WBGT <10°C , Green = WBGT 10-18°C , Yellow = WBGT 18-23°C , Red = WBGT 23-28°C , Black = WBGT >28°C |
| **% CR**        | Percent off current course record for gender                                               |
| **Td, °C**      | Dry bulb temperature in Celsius                                                            |
| **Tw, °C**      | Wet bulb temperature in Celsius                                                            |
| **%rh**         | Percent relative humidity                                                                  |
| **Tg, °C**      | Black globe temperature in Celsius                                                         |
| **SR W/m²**     | Solar radiation in Watts per meter squared                                                 |
| **DP**          | Dew Point in Celsius                                                                       |
| **Wind**        | Wind speed in Km/hr                                                                        |
| **WBGT**        | Wet Bulb Globe Temperature                                                                 |

Note that the variable `WBGT` is actually a composite index that combines the effects of `Td`, `Tw`, and `Tg`, which means we can ignore the three variables when analyzing the data.

$$
WBGT = 0.7 \times Tw + 0.2 \times Tg + 0.1 \times Td
$$

This data contains of 11073 observations and 12 variables. The data documented the 5 major races form year 1993 to 2016, and each observation represents the average performance of a specific age in a particular race during a specific year. It should be noted that in this dataset, only one set of weather data is recorded for each race.

### Course Record Data

This dataset contains the course record for each race grouped by sex documented in the Marathon Data. The dataset includes the following columns:

| Parameter       | Coding details                                                                            |
|-----------------|-------------------------------------------------------------------------------------------|
| **Race**        | B = Boston Marathon , C = Chicago Marathon , NY = New York City Marathon , TC = Twin Cities Marathon (Minneapolis, MN) , D = Grandma’s Marathon (Duluth, MN) |
| **Sex/Gender**  | 0 = Identified as Female , 1 = Identified as Male                                       |
| **Year**        | Year of the marathon                                                                      |
| **CR**          | Current course record for gender                                               |

Different from the Marathon Data, the `CR` in this dataset is in hours, which means we can calculate the completion time of each runner by multiplying the CR percentage in the Marathon Data with the CR in this dataset.

# Data Preprocessing

## Data Manipulation

For clarity, we firstly rename the `Race` column in the Marathon Data as well as the Course Record Data to the full name of the marathon. And since we are using two datasets, we need to merge them based on the `Race`, `Year`, and `Sex` columns. After merging, we now have a united dataset that contains 15 variables and 11073 observations in total.

And then, condiering of the nature of the variables and the analysis we are going to perform, we convert the `Year`, `Race`, `Sex`, and `Flag` columns to factors. We also created a new column `Age_group` by grouping the `Age` column into 10-year intervals. This step is essential trying to factorize the `Age` column.

Most importantly, we would like to convert the `CR` in the Course Record Data to seconds. The process is simple, we first convert the `CR` to a period object and then convert it to seconds. After that, we can calculate the completion time of each runner by multiplying the CR percentage in the Marathon Data with the CR in this dataset. The calculation formula is as follows:

$$
CR_{adjusted} = (1 + CR_{PERCENTAGE} \times 0.01) \times CR
$$

```{r data_intro}
# rename the column names that are too long to follow.
colnames(marathon_data)[1] <- "Race"
colnames(marathon_data)[3] <- "Sex"
colnames(marathon_data)[5] <- "Age"
colnames(marathon_data)[6] <- "CR_PERCENTAGE"
colnames(marathon_data)[7] <- "TD"
colnames(marathon_data)[8] <- "TW"
colnames(marathon_data)[9] <- "RH"
colnames(marathon_data)[10] <- "TG"
colnames(marathon_data)[11] <- "SR"

# data type conversion
marathon_data$Year <- as.factor(marathon_data$Year)
marathon_data$Race <- as.factor(marathon_data$Race)
marathon_data$Sex <- as.factor(marathon_data$Sex)
marathon_data$Flag <- as.factor(marathon_data$Flag)

marathon_data$Flag[marathon_data$Flag == ""] <- NA

# replace marathon name with code name in course_record
course_record$Race[course_record$Race == "B"] <- 0
course_record$Race[course_record$Race == "C"] <- 1
course_record$Race[course_record$Race == "NY"] <- 2
course_record$Race[course_record$Race == "TC"] <- 3
course_record$Race[course_record$Race == "D"] <- 4
course_record$Race <- as.factor(course_record$Race)

# replace gender in course_record
course_record$Gender[course_record$Gender == "M"] <- 1
course_record$Gender[course_record$Gender == "F"] <- 0
course_record$Gender <- as.factor(course_record$Gender)
colnames(course_record)[4] <- "Sex"

# Transform records in course_record into seconds
course_record$CR <- period_to_seconds(hms(course_record$CR))

# Join course_record and marathon_data
marathon_data <- merge(marathon_data, course_record, by = c("Race", "Year", "Sex"))

# calculate the record of each runner
marathon_data$CR <- (1 + marathon_data$CR_PERCENTAGE * 0.01) * marathon_data$CR

marathon_data <- marathon_data %>%
  mutate(Race = case_when(
    Race == 0 ~ "Boston",
    Race == 1 ~ "Chicago",
    Race == 2 ~ "NYC",
    Race == 3 ~ "Twin Cities",
    Race == 4 ~ "Grandma"
  ),
  Sex = case_when(
    Sex == 1 ~ "Male",
    Sex == 0 ~ "Female"
  )) %>%
  mutate(Age_group = cut(Age, breaks = seq(0, 100, by = 10), right = FALSE, 
                         labels = c("0-9", "10-19", "20-29", "30-39", "40-49", 
                                    "50-59", "60-69", "70-79", "80-89", "90-99")))

```

## Data Quality Check

Before we start the analysis, we need to check the data quality. We first check for missing values and patterns in the dataset. The missing values are visualized using the `vis_miss` function from the `naniar` package. The plot shows that there are missing values in the weather related columns, and this missingness seems to have a very clear pattern. Based on this pattern, we can assume boldly that the missing values are not missing at random, but are related to specific races.

```{r missing_pattern, fig.width = 15}
# Check for missing values and patterns
miss_plot <- vis_miss(marathon_data)
ggsave("../Plots/missing_values_plot.png", plot = miss_plot, width = 15, dpi = 300)
miss_plot

```

In order to veryify our assumption, we calculate the missing percentage of weather data in each marathon by year. The table below shows that the missing percentage of most of the races are 0, however, for races held in 2011 (Chicago, NYC, and Twin Cities) as well as the one held in 2012 (Grandmas), the missing percentage is 100%. This confirms our assumption that the missing values are related to specific races. It would be a wise choice to remove all of those races from our dataset. To be noted that the NA value in the table means there are no races held in that year.

```{r missing_percentage}
# Check the missing percentage of weather data in each marathon by year
marathon_data %>%
  group_by(Race, Year) %>%
  summarise(missing_percentage = sum(is.na(Flag)) / n()) %>%
  pivot_wider(names_from="Race", values_from = missing_percentage) %>%
  arrange(Year) %>%
  replace_na(list(Boston = 0, Chicago = 0, NYC = 0, `Twin Cities` = 0, Grandmas = 0)) %>%
  kable(caption = "Missing Percentage of Weather Data in Each Marathon by Year")

```

```{r remove_missing}
# remove missing data
marathon_data <- marathon_data %>% filter(!is.na(Flag))

```

And we also want to check the performance distribution of each race by year, since although the weather condition may vary from year to year, the performance of runners may not change significantly within the same track. As we can see in the plot below, despite some disturbances, the performance of runners tend to stay stable over the years. The difference in performance might be due to the different weather conditions in different years. Overall, the stability of the performance indicates that the dataset is reliable for analysis.

```{r completion_time_race, fig.width = 8, fig.height = 5}
completion_time_race <- ggplot(marathon_data, aes(x = Year, y = CR)) +
  geom_boxplot(aes(fill = Race), alpha = 0.5) +
  stat_summary(fun = "mean", geom = "point", shape = 23, size = 1, fill = "red") +
  stat_summary(fun = "mean", geom = "line", aes(group = 1), color = "red") +
  facet_wrap(~ Race) +
  labs(title = "CR Distribution by Year and Race",
       x = "Year",
       y = "Completion Time (CR)") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),
    legend.position = "none"
  )
ggsave("../Plots/completion_time_race.png", plot = completion_time_race, width = 10, height = 8, dpi = 300)
completion_time_race

```

Another factor might affect the result of the analysis is `age`. In a balanced dataset, we would expect the number of participants in each age group to be roughly the same. To check this, we count the number of participants in each age group for each races. The table shows a pattern that for each race, participants between age 20 to 79 are the most common and also balanced, while the number of participants in the 10-19, 80-89 and 90-99 age groups are relatively small. This suggests that the inference results obtained from the 10-19, 80-89 and 90-99 age groups may not be as reliable as those obtained from the 20-79 age groups. Moreover, the number of participants in the 90-99 age group is extremely small, so we decide to merge it with the 80-89 age group to become the 80-99 age group.

Similarly, we would hope that participants' gender is balanced in the dataset. From the table below, we can tell the Female:Male portion is roughly equal to 1 in all of the races, which is a good feature for our analysis.

```{r age_sex_distribution}
tbl_summary(
  marathon_data %>% select(Race, Age_group, Sex),
  by = Race,
    statistic = list(
    Age_group ~ "{n} ({p}%)",
    Sex ~ "{n} ({p}%)"
  )
) %>%
  modify_header(label = "**Age Group**") %>%
  modify_caption("**Number of Participants by Age Group, Sex and Race**") 
```

```{r participants_age_plot, include=FALSE}
participants_age_plot <- ggplot(marathon_data, aes(x = Age_group, fill = Age_group)) +
  geom_bar() +
  facet_wrap(~ Race) +
  scale_fill_viridis_d() +
  labs(title = "Number of Participants by Age Group for Each Race",
       x = "Age Group",
       y = "Number of Participants",
       fill = "Age Group") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("../Plots/participants_age_plot.png", plot = participants_age_plot, width = 10, height = 8, dpi = 300)
participants_age_plot

```

```{r merge_age_group}
marathon_data <- marathon_data %>%
  mutate(Age_group = if_else(Age_group == "90-99", "80-99", Age_group)) %>%
  mutate(Age_group = if_else(Age_group == "80-89", "80-99", Age_group))
```

```{r sex_distribution_race, include=FALSE}
sex_distribution_race <- ggplot(marathon_data, aes(x = Sex, fill = Sex)) +
  geom_bar(position = "dodge", alpha = 0.7) +
  facet_wrap(~ Race, scales = "free_y") +
  labs(title = "Sex Distribution by Race",
       x = "Sex",
       y = "Count",
       fill = "Sex") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(face = "italic"),
    legend.position = "none"
  )
ggsave("../Plots/sex_distribution_race.png", plot = sex_distribution_race, width = 10, height = 8, dpi = 300)
sex_distribution_race

```

We also want to check the correlation between the weather variables. The correlation plot below shows that `DP` is highly correlated with `WBGT`, which means we can ignore the `DP` variable when analyzing the data. And since the `WBGT` is a composite index that combines the effects of `Td`, `Tw`, and `Tg`, all of those variables are highly correlated with `WBGT`, meaning that they can be ignored as well.

```{r cor_plot, fig.width = 8, fig.height = 5}
cor_plot <- ggpairs(marathon_data %>% select(TD, TW, RH, TG, SR, DP, Wind, WBGT)) + ggtitle("Correlation Plot of Weather Variables")
ggsave("../Plots/cor_plot.png", plot = cor_plot, width = 10, height = 8, dpi = 300)
cor_plot

```

# Data Analysis

## Inner Factors Analysis

A very instinctive thought is that the completion time of a marathon is influenced by gender. To verify this, we first plot the distribution of completion time percentage among Female and Male, and find that in each races, males tend to have a lower completion time. And we can also observe a distribution pattern that the completion time for both male and female runners is heavily skewed, which means that most of the runners have a completion time close to the course record. This suggests that our runners are generally well-trained and have a good performance.

```{r cr_distribution_plot, fig.width = 6, fig.height = 3}
cr_distribution_plot <- ggplot(marathon_data, aes(x=Race, y = CR_PERCENTAGE, fill=Sex)) +
  geom_split_violin() +
  labs(title = "Distribution of Completion Time Percentage",
       y = "CR Percentage") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
ggsave("../Plots/cr_distribution_plot.png", plot = cr_distribution_plot, width = 8, height = 5, dpi = 300)
cr_distribution_plot

```

Next, we want to explore the effect of age on marathon performance. From the plot below, we can not only observe the fact that female runners are tend to run slower than male runners, but we can also observe that in each cases, no matter male or female, the completion time decreases first and then increases with age. And people around their 30s tend to have the best performance. This suggests that the completion time of a marathon is influenced by age, and the effect of age on completion time is not linear.

```{r age_effect_plot, fig.width = 7, fig.height = 4}
age_effect_plot <- ggplot(marathon_data, aes(x = Age, y = CR, color = Sex)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess", se = TRUE) +
  facet_wrap(~ Race, scales = "free_y") +
  labs(title = "Effect of Age on Marathon Performance by Race",
       x = "Age (yrs)", 
       y = "Best Time (CR)",
       color = "Sex") +
  theme_minimal() + 
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1),
    legend.position = "top"
  )
ggsave("../Plots/age_effect_plot.png", plot = age_effect_plot, width = 10, height = 8, dpi = 300)
age_effect_plot

```

## Weather (Outer) Factors Analysis

Both of `Age` and `Sex` can be considered as inner factors that affect the completion time of a marathon. We also care about the outer factors such as weather condition. Multiple weather variables are recorded in the dataset, including `RH`, `SR`, `DP`, `Wind`, and `WBGT`. In the following section, we will analyze the effect of these weather variables on marathon performance, and also explore the interaction between weather variables and inner factors.

We first want to focus on the effect of `WBGT` on marathon performance. `WBGT` is a composite index that combines the effects of `Td`, `Tw`, and `Tg`. Conceputally, the `WBGT` is an index used to estimate the effect of temperature, humidity, wind speed, and solar radiation on humans, typically to assess heat stress during physical activities in outdoor environments. That suggests the higher the `WBGT`, the more difficult for runners to finish the marathon. 

In order to prove our assumption, we plot the effect of `WBGT` on completion time by sex. However, instead of using `WBGT` directly, we use the `Flag` column to represent the `WBGT` level. The `Flag` column is a categorical variable that represents the `WBGT` level, with White representing the lowest `WBGT` level and Black representing the highest `WBGT` level. In the following plot, each of the plot represents an observation, and the color of the plot represents the `Flag` level. To better read the result, we also add linear regression line to each plot. 

By interpreting the plot, we can tell that in general cases, the worse the `WBGT` level, the higher the completion time. In detail, we found that the `WBGT` level do have different effect for different age groups as well as gender. To be note that, the wider the space between two regression lines, the more significant the effect of `WBGT` level on completion time. In that case, we can tell the `WBGT` level has a more significant effect on male than female. And looking at the difference among age groups, we found that the `WBGT` has more effect on elder runners than younger runners. Additionaly, we see intersection between the regression lines around age 75, we think that might be due to the small number of participants in the 70-79 age group, causing the result to be less reliable, the larger standard error of the regression line showing in the plot also suggests this assumption.

```{r wgbt_effect, fig.width = 8, fig.height = 4}
# WGBT effects
flag_colors <- c("Green" = "darkgreen", 
                 "Yellow" = "orange", 
                 "Red" = "darkred", 
                 "White" = "darkgrey")


wgbt_effect <- marathon_data %>%
  ggplot(aes(x = Age, y = CR_PERCENTAGE, color = Flag)) +
  facet_wrap(~ Sex, scales = "fixed") +
  geom_point(alpha = 0.1) +
  geom_smooth(aes(group = Flag, color = Flag), se = T, size=0.5) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = 100, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = 150, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = 200, linetype = "dashed", color = "blue") +
  scale_color_manual(values = flag_colors) +
  labs(title = "WGBT Effect on Completion Time by Age and Sex",
       x = "Age",
       y = "Percenatge of Completion Time",
       color = "Flag") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
ggsave("../Plots/wgbt_effect.png", plot = wgbt_effect, width = 10, height = 8, dpi = 300)
wgbt_effect

```

```{r weather_effect, fig.width = 20, fig.height = 30}
age_group_colors <- c("0-9" = "#1b9e77", 
                      "10-19" = "#d95f02", 
                      "20-29" = "#7570b3", 
                      "30-39" = "#e7298a", 
                      "40-49" = "#98c61e", 
                      "50-59" = "#e6ab02", 
                      "60-69" = "#a6761d", 
                      "70-79" = "#666666", 
                      "80-99" = "#1f78b4")

# RH Effects
RH_sex <- marathon_data %>%
      ggplot(aes(x = as.factor(round(RH, 2)), y = CR_PERCENTAGE, color = Sex)) +
      geom_boxplot(alpha = 0.7) +
      geom_smooth(aes(group = Sex), se = FALSE) +
      labs(title = "RH Effect on Marathon Performance by Sex",
           x = "RH",
           y = "Completion Time") +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 90)
      )

RH_age <- marathon_data %>%
      ggplot(aes(x = as.factor(round(RH, 2)), y = CR_PERCENTAGE, fill = Age_group, color = Age_group)) +
      geom_point(alpha = 0.2) +
      geom_smooth(aes(group = Age_group, color = Age_group), se = T) + 
      scale_fill_manual(values = age_group_colors) +
      scale_color_manual(values = age_group_colors) +
      labs(title = "RH Effect on Marathon Performance by Age",
           x = "RH",
           y = "Percentage of Completion Time",
           fill = "Age Group",
           color = "Age Group") + 
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 90)
      )

# Wind Effects
Wind_sex <- marathon_data %>%
      ggplot(aes(x = as.factor(round(Wind, 2)), y = CR_PERCENTAGE, color = Sex)) +
      geom_boxplot(alpha = 0.7) +
      geom_smooth(aes(group = Sex), se = FALSE) +
      labs(title = "Wind Effect on Marathon Performance by Sex",
           x = "Wind",
           y = "Completion Time") +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 90)
      )

Wind_age <- marathon_data %>%
      ggplot(aes(x = as.factor(round(Wind, 2)), y = CR_PERCENTAGE, fill = Age_group, color = Age_group)) +
      geom_point(alpha = 0.2) + 
      geom_smooth(aes(group = Age_group, color = Age_group), se = T) + 
      scale_fill_manual(values = age_group_colors) +
      scale_color_manual(values = age_group_colors) +
      labs(title = "Wind Effect on Marathon Performance by Age",
           x = "Wind",
           y = "Percentage of Completion Time",
           fill = "Age Group",
           color = "Age Group") + 
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 90)
      )

# SR Effects
SR_sex <- marathon_data %>%
      ggplot(aes(x = as.factor(round(SR, 2)), y = CR_PERCENTAGE, color = Sex)) +
      geom_boxplot(alpha = 0.7) +
      geom_smooth(aes(group = Sex), se = FALSE) +
      labs(title = "SR Effect on Marathon Performance by Sex",
           x = "SR",
           y = "Completion Time") +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 90)
      )

SR_age <- marathon_data %>%
      ggplot(aes(x = as.factor(round(SR, 2)), y = CR_PERCENTAGE, fill = Age_group, color = Age_group)) +
      geom_point(alpha = 0.2) + 
      geom_smooth(aes(group = Age_group, color = Age_group), se = T) + 
      scale_fill_manual(values = age_group_colors) +
      scale_color_manual(values = age_group_colors) +
      labs(title = "SR Effect on Marathon Performance by Age",
           x = "SR",
           y = "Percentage of Completion Time",
           fill = "Age Group",
           color = "Age Group") + 
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 90)
      )

weather_effect <- (RH_sex | RH_age) / (Wind_sex | Wind_age) / (SR_sex | SR_age) +
  plot_layout(guides = "collect", axis_titles = "collect") &
  theme(legend.position = 'bottom')
ggsave("../Plots/weather_effect.png", plot = weather_effect, width = 20, height = 30, dpi = 300)
weather_effect

```


```{r}
# RH model
RH_model <- glm(CR_PERCENTAGE ~ RH + Sex + Age, data = marathon_data)
kable(summary(RH_model)$coefficients, caption = "RH Model Coefficients")

# SR model
SR_model <- glm(CR_PERCENTAGE ~ SR + Sex + Age, data = marathon_data)
kable(summary(SR_model)$coefficients, caption = "SR Model Coefficients")

# DP model
DP_model <- glm(CR_PERCENTAGE ~ DP + Sex + Age, data = marathon_data)
kable(summary(DP_model)$coefficients, caption = "DP Model Coefficients")

# Wind model
Wind_model <- glm(CR_PERCENTAGE ~ Wind + Sex + Age, data = marathon_data)
kable(summary(Wind_model)$coefficients, caption = "Wind Model Coefficients")

# Flag model
Flag_model <- glm(CR_PERCENTAGE ~ Flag + Sex + Age, data = marathon_data)
kable(summary(Flag_model)$coefficients, caption = "Flag Model Coefficients")

# WBGT model
WBGT_model <- glm(CR_PERCENTAGE ~ WBGT + Sex + Age, data = marathon_data)
kable(summary(WBGT_model)$coefficients, caption = "WBGT Model Coefficients")

```

```{r}
# linear model
lm_model_1 <- glm(CR_PERCENTAGE ~ RH + SR + DP + Wind + WBGT + Sex + Age, data = marathon_data)
kable(summary(lm_model_1)$coefficients, caption = "Model with WBGT Coefficients")

lm_mode_2 <- glm(CR_PERCENTAGE ~ RH + SR + DP + Wind + Flag + Sex + Age, data = marathon_data)
kable(summary(lm_mode_2)$coefficients, caption = "Model with Flag Coefficients")

```

# Discussion

# References

# Code Appendix

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}

```
